---
title: "EDA Mid_term"
author: "Bharat P"
date: "2022-10-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
```
For the purpose of analysis, the stock data of each month is considered from 2012-2021 for the following 14 metals/mining stocks. In which the first 7 of them are Indian Companies and the other 7 are American Companies.
```{r}
Companies=c('TATA STEEL','HINDALCO','STEEL AUTHORITY OF INDIA (SAIL)','NATIONAL ALUMINIUM COMPANY (NALCO)','VEDANTA','JSW STEEL','NATIONAL MINERAL DEVELOPMENT CORP (NMDC)','CAMECO','STEEL DYNAMICS','UNITED STATES STEEL CORPORATION','NUCOR CORP','CLEAVELAND CLIFFS','VALE','COMMERCIAL METAL COMPANY')
SLNo=c(1:14)
stock_tab=data.frame(SLNo,Companies)
(stock_tab) %>%
  kbl() %>%
  kable_material(c("striped", "hover"))
```


Initially, we import the CSV files containing the stock data of all the  business days in a month. The CSV file contains the Open, Close, High and Low prices along with the adjusted Close Price and Volume of considered stock.
The below table shows the contents of the DataFrame
```{r}
Stock_Data=read.csv('TATASTEEL.NS-2021-1.csv')
head(Stock_Data) %>%
  kbl() %>%
  kable_material(c("striped", "hover"))
```

