---
title: "EDA Midterm Output code"
author: "Bharat P"
date: "2022-11-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("./EDA_code.R")
```

The function below is in the function source file "EDA code.R" and is presented here for better understanding

```{r eval=FALSE}

# A function to read all csv files in the folder 
stock_dat<-function(file_path) # Function that takes the file path as input
  {
  file_paths=fs::dir_ls(file_path) # Gets the file path of all files
    ccsv=list()
    for (i in seq_along(file_paths)) # iterating through the each file path 
      {
    ccsv[[i]]<-data.frame(read.csv(file=file_paths[i])) # putting the file contents in a list
    }
  return(ccsv)
```


Passing the file path to get the csv file from each folder where the stock data is contained.

**Make sure you change the file paths in the below function to where the data files are housed, before executing**
```{r}
#Make sure you change the file paths in the below function to where the data files are housed, before executing

TS_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/Tata Steel")   
X_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/US Steel")
NLCO_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/NALCO")  
NUC_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/Nucor")
HLCO_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/Hindalco") 
CCJ_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/Cameco")
SAIL_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/SAIL")  
CLF_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/Cleaveland Cliffs")
JSW_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/JSW")   
CMC_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/Commercial metals company")
NMDC_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/NMDC")
STLD_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/Steel Dynamics")
VED_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/Vedanta")   
VALE_csv=stock_dat("C:/Users/Bharat P/Documents/Data Folder/VALE")
```






The below function takes in the stock data and expected change as inputs and gives out the success, failure and no opportunity counts.


 The function below is in the source file `EDA_code.R`  
```{r eval=FALSE}
stock_stats=function(list_data_frame,u_change)
{
  First_Day_down=numeric(100)   # Initializing the arrays to store the number of success and failures
  Second_Day_down=numeric(100)
  Third_Day_down=numeric(100)
  First_Day_up=numeric(100)
  Second_Day_up=numeric(100)
  Third_Day_up=numeric(100)
  failure=numeric(100)
  no_opportunity=numeric(100)
  k=numeric(1)                
  
  for (i in 1:length(list_data_frame)){        # Iterating through each dataframe for individual stock
    Datee=as.Date(list_data_frame[[i]]$Date,format="%Y-%m-%d") # Getting the dates in each month
    Day=format(Datee,"%d")                     # Extracting only days from the date
    Day=as.integer(Day)-13                     # Converting the day type to integer and subtracting 13 
    ind=numeric(1)
    for (j in 1:(length(Day)-2)){              # Looping through the extracted (days -13)
      if ((Day[j]*Day[j+1])<=0){               # If this criteria is satisfied we get 13th 
        ind[1]<-j                              # Getting the index of 13th
      } else{                                  # If the condition is not satisfied the loop proceeds to next iteration
        next
      }
    }
    
    
    t1=((list_data_frame[[i]]$High[ind+1])-(list_data_frame[[i]]$High[ind]))/((list_data_frame[[i]]$Low[ind+1])-(list_data_frame[[i]]$Low[ind]));     # ((H2-H1)/(L2-L1)) criteria
    t2=((list_data_frame[[i]]$High[ind+3])-(list_data_frame[[i]]$High[ind+2]))/((list_data_frame[[i]]$Low[ind+3])-(list_data_frame[[i]]$Low[ind+2])); #  ((H4-H3)/(L4-L3)) criteria
    
    if ((t1>0 & t2>0 & is.nan(t1)==FALSE & is.nan(t2)==FALSE)) # Condition to check Gann's triangles formation
      {
      if (((list_data_frame[[i]]$Low[ind+4])<(list_data_frame[[i]]$Low[ind+3]))&((list_data_frame[[i]]$High[ind+4])<(list_data_frame[[i]]$High[ind+3]))) # Condition to check if trade is favourable in downward direction
        {                                                                                                                                     
        if (((-1*((list_data_frame[[i]]$Low[ind+5])-(list_data_frame[[i]]$Low[ind+3])))>=((u_change/100)*list_data_frame[[i]]$Low[ind+3])) || # Checking if the stock crossed u_change from L4 on 1st day
            ((-1*((list_data_frame[[i]]$Low[ind+6])-(list_data_frame[[i]]$Low[ind+3])))>=((u_change/100)*list_data_frame[[i]]$Low[ind+3])) || # Checking if the stock crossed u_change from L4 on 2nd day
            ((-1*((list_data_frame[[i]]$Low[ind+7])-(list_data_frame[[i]]$Low[ind+3])))>=(u_change/100)*list_data_frame[[i]]$Low[ind+3])) {   # Checking if the stock crossed u_change from L4 on 3rd day
          
          if (((-1*((list_data_frame[[i]]$Low[ind+5])-(list_data_frame[[i]]$Low[ind+3])))>=((u_change/100)*list_data_frame[[i]]$Low[ind+3]))==TRUE){
             First_Day_down=append(First_Day_down,1)                                                                                                 # Appending the array if the 1st day condition is satisfied
          }
          else if (((-1*((list_data_frame[[i]]$Low[ind+6])-(list_data_frame[[i]]$Low[ind+3])))>=((u_change/100)*list_data_frame[[i]]$Low[ind+3]))==TRUE){
            Second_Day_down=append(Second_Day_down,1)                                                                                                # Appending the array if the 2nd day condition is satisfied
            k=1
          } 
          else if (((-1*((list_data_frame[[i]]$Low[ind+7])-(list_data_frame[[i]]$Low[ind+3])))>=((u_change/100)*list_data_frame[[i]]$Low[ind+3]))==TRUE){
            Third_Day_down=append(Third_Day_down,1)                                                                                                  # Appending the array if the 3rd day condition is satisfied
          }
        } else{
          failure=append(failure,1)   # If none of the condition is satisfied then counting it as a failure
        }
      }
      else if (((list_data_frame[[i]]$Low[ind+4])>(list_data_frame[[i]]$Low[ind+3]))&((list_data_frame[[i]]$High[ind+4])>(list_data_frame[[i]]$High[ind+3]))) # Condition to check if trade is favourable in upward direction
      {
        if (((((list_data_frame[[i]]$High[ind+5])-(list_data_frame[[i]]$High[ind+3])))>=((u_change/100)*list_data_frame[[i]]$High[ind+3])) ||           # Checking if the stock crossed u_change from L4 on 1st day
            ((((list_data_frame[[i]]$High[ind+6])-(list_data_frame[[i]]$High[ind+3])))>=((u_change/100)*list_data_frame[[i]]$High[ind+3])) ||           # Checking if the stock crossed u_change from L4 on 2nd day
            ((((list_data_frame[[i]]$High[ind+7])-(list_data_frame[[i]]$High[ind+3])))>=(u_change/100)*list_data_frame[[i]]$High[ind+3])) {             # Checking if the stock crossed u_change from L4 on 3rd day
          if (((((list_data_frame[[i]]$High[ind+5])-(list_data_frame[[i]]$High[ind+3])))>=((u_change/100)*list_data_frame[[i]]$High[ind+3]))==TRUE){
            First_Day_up=append(First_Day_up,1)                                                                                                         # Appending the array if the 1st day condition is satisfied   
          }
          else if (((((list_data_frame[[i]]$High[ind+6])-(list_data_frame[[i]]$High[ind+3])))>=((u_change/100)*list_data_frame[[i]]$High[ind+3]))==TRUE){
            Second_Day_up=append(Second_Day_up,1)                                                                                                       # Appending the array if the 2nd day condition is satisfied
          } else if (((((list_data_frame[[i]]$High[ind+7])-(list_data_frame[[i]]$High[ind+3])))>=((u_change/100)*list_data_frame[[i]]$High[ind+3]))==TRUE){
            Third_Day_up=append(Third_Day_up,1)                                                                                                         # Appending the array if the 3rd day condition is satisfied        
          }
        } else{
          failure=append(failure,1)      # If none of the condition is satisfied then counting it as a failure
        }
      } else{
        no_opportunity=append(no_opportunity,1)  # If the criteria to get the direction is not satisfied then it is counted as no opportunity
      }
    } else {
      no_opportunity=append(no_opportunity,1)  # If the criteria to get the direction is not satisfied then it is counted as no opportunity
    }
  }
  sum_succ=(sum(First_Day_down)+sum(Second_Day_down)+sum(Third_Day_down)+   # Summing all the successes
              sum(First_Day_up)+sum(Second_Day_up)+sum(Third_Day_up))
  sum_failure=(sum(failure))                                            # Summing the failures
  sum_no=(sum(no_opportunity))                                          # Summing the no opportunity 
  
  f_success<<-sum(First_Day_up)+sum(First_Day_down)                     # Summing the first day success 
  s_success<<-sum(Second_Day_up)+sum(Second_Day_down)                   # Summing the second day success
  T_success<<-sum(Third_Day_up)+sum(Third_Day_down)                     # Summing the third day success
  return(c(sum_succ,sum_failure,sum_no))                                # Returning a vector of total success, failure and no opportunity for a stock
}
```

Passing the CSV files of the stocks into the function `stock_stats` by setting u_change=2 for all the stocks
```{r}
TS_stats=stock_stats(TS_csv,2)   
X_stats=stock_stats(X_csv,2)
NLCO_stats=stock_stats(NLCO_csv,2)  
NUC_stats=stock_stats(NUC_csv,2)
HLCO_stats=stock_stats(HLCO_csv,2) 
CCJ_stats=stock_stats(CCJ_csv,2)
SAIL_stats=stock_stats(SAIL_csv,2)  
CLF_stats=stock_stats(CLF_csv,2)
JSW_stats=stock_stats(JSW_csv,2)   
CMC_stats=stock_stats(CMC_csv,2)
NMDC_stats=stock_stats(NMDC_csv,2)
STLD_stats=stock_stats(STLD_csv,2)
VED_stats=stock_stats(VED_csv,2)   
VALE_stats=stock_stats(VALE_csv,2)
```

```{r}
# Creating a dataframe to combine the results of all the stocks
SF_Data=data.frame(TS_stats,X_stats,NLCO_stats,NUC_stats,HLCO_stats,CCJ_stats,SAIL_stats,CLF_stats,
                   JSW_stats,CMC_stats,NMDC_stats,STLD_stats,VED_stats,VALE_stats)
SF_Data=t(SF_Data) # Transposing the Dataframe

# Renaming the rows of the dataframe
row.names(SF_Data)<-c('TATASTEEL','US STEEL','NALCO','NUCOR','HINDALCO','CAMECO','SAIL',
                      'CLEVELAND','JSW STEEL','COMM.METAL','NMDC','STEEL DYN','VEDANTA','VALE')

# Renaming the columns of the dataframe

colnames(SF_Data)<-c('Success','Failure','No opportunity')

SF_Data
```

